\bf Faster Neural Machine Translation Inference

### 2018-02-02 fast-beam/fast-beam.tex
fast beam paper

After some experimentation, we decided to fully fill the decoding batch only when it is at least half empty, rather than whenever a sentence has completed.

@@

\section{Conclusion}

>>>>

After some experimentation, we decided to top-up the decoding batch only when it is at least half empty, rather than whenever a sentence has completed.

@@

\section{Conclusion and Future Work}

We have presented two methods for faster deep-learning inference, targeted at neural machine translation.

The first method focused on output layer of the neural network which accounts for a large part of the running time of the NMT model. By fusing the output layer with the beam search, we are able to increase translation speed by up to 41\%.

The second method replaces the mini-batching algorithm with one that avoids decoding with a small number of sentences, maximizing the parallel processing potential of GPUs. For certain scenarios, this increases translating  speed by up to 12\%.

For future work, we would like to apply our optimization for other NLP and deep-learning tasks. We are also interested in further optimization of the output layer in NMT, specifically the matrix multiplication which currrently take up ??? of the translation time.
